A Plasma Torus Around a Young Low-Mass Star

### 2025-04-23 paper/ms.tex
update

\begin{figure}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.47\textwidth]{figures/sf3.pdf}
		}
		\subfloat{
			\includegraphics[width=0.47\textwidth]{figures/sf2.pdf}
		}
	\end{center}
	\vspace{0.0cm}
  \caption{{\bf TIC\,141146667 age diagnostics.}
  {\it Left:} Dereddened Gaia DR3 color vs.~absolute magnitude diagram of
  TIC\,141146667 and comparison samples. 
  TIC\,141146667 is on the pre-main sequence; stars with the same color
  on the main sequence are $\approx$1.5\,magnitudes
  fainter.  The star's location in this diagram suggests an
  age of 30-150\,Myr. 
  {\it Right:} An upper limit on photospheric lithium for TIC\,141146667
  (green triangle) yields a lower bound on the star's age of
  $\gtrsim$20\,Myr.  Comparison stars are from the Gaia-ESO survey
  \citep{Jeffries2023}; rich clusters in each age bin include NGC\,2264
  (4.5\,Myr), $\lambda$~Ori (8.7\,Myr), ${\rm \gamma}^2$\,Vel
  (16.4\,Myr), NGC\,2547 (35.0\,Myr), IC\,2602 and IC\,2391 (42.0\,Myr),
  and NGC\,2451A (50.0\,Myr). }
  \label{fig:age_diagnostics}
\end{figure}

@@

\begin{figure*}[!t]
  \centering
  \includegraphics[width=\textwidth]{figures/sf5.pdf}
  \vspace{-0.25cm}
  \caption{{\bf Time evolution of the Keck/HIRES spectra
  from 17 February 2024.}  We made this plot by applying a windowed
  outlier rejection to remove cosmic rays and then smoothing each
  spectrum with a Gaussian filter.  The horizontal axis shows the
  velocity relative to each line's rest wavelength, normalized by the
  stellar equatorial velocity.  H$\alpha$ is the only Balmer line to
  show periodic variability similar to Figure~\ref{fig:spec}.
	The He 5876\,\AA\ line shows a time-dynamic blueshift.  Li 6708\,\AA\ shows
	no obvious absorption. }
  \label{fig:hirescuts}
\end{figure*}

>>>>

\begin{figure}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.46\textwidth]{figures/sf3.pdf}
		}
		\subfloat{
			\includegraphics[width=0.47\textwidth]{figures/sf2.pdf}
		}
	\end{center}
	\vspace{-0.3cm}
  \caption{{\bf TIC\,141146667 age diagnostics.}
  {\bf a,} Dereddened Gaia DR3 color vs.~absolute magnitude for
  TIC\,141146667, USco (8\,Myr), IC\,2602 (40\,Myr), the Pleiades
  (112\,Myr) and stars within 100\,pc. 
  The location of TIC\,141146667 in this diagram suggests an age of
  30-150\,Myr. 
  {\bf b,} An upper limit on photospheric lithium for TIC\,141146667
  (green triangle) yields a lower bound on the star's age of
  $\gtrsim$20\,Myr.  Comparison stars are from the Gaia-ESO survey
  \citep{Jeffries2023}; rich clusters in these data include NGC\,2264
  (4.5\,Myr), $\lambda$~Ori (8.7\,Myr), ${\rm \gamma}^2$\,Vel
  (16.4\,Myr), NGC\,2547 (35.0\,Myr), IC\,2391 (42.0\,Myr),
  and NGC\,2451A (50.0\,Myr). }
  \label{fig:age_diagnostics}
\end{figure}

@@

\begin{figure*}[!t]
  \centering
  \includegraphics[width=\textwidth]{figures/sf5.pdf}
  \vspace{-0.5cm}
  \caption{{\bf Time evolution of the Keck/HIRES spectra
  from 17 February 2024.}  We made this plot by applying a windowed
  outlier rejection to remove cosmic rays and then smoothing each
  spectrum with a Gaussian filter.  The horizontal axis shows the
  velocity relative to each line's rest wavelength, normalized by the
  stellar equatorial velocity.  H$\alpha$ is the only Balmer line to
  show periodic variability similar to Figure~\ref{fig:spec}.
	The He 5876\,\AA\ line shows a time-dynamic blueshift.  Li 6708\,\AA\ shows
	no obvious absorption. }
  \label{fig:hirescuts}
\end{figure*}
